### 2023-08-08 proofs/main.tex
wip: leftovers

\newcommand{\depth}[1]{\mathsf{depth}(#1)}

@@

\subsection{Grammar}
\ottgrammartabular{
  \ottiP\ottinterrule
  \ottiN\ottinterrule
  \ottv\ottinterrule
  \ottc\ottinterrule
}

@@

@@

@@

\subsection{Substitution}
\input{../_build/_gen/tex/subst-lemmas.tex}

>>>>

\newcommand{\depth}[1]{\mathsf{depth}(#1)}
\newcommand{\size}[1]{\mathsf{size}(#1)}

@@

\subsection{Grammar}
We assume that there is an infinite set of positive and 
negative \emph{type} variables. Positive type variables are denoted as 
$[[α⁺]]$, $[[β⁺]]$, $[[γ⁺]]$, etc.
Negative type variables are denoted as $[[α⁻]]$, $[[β⁻]]$, $[[γ⁻]]$, etc.
We assume there is an infinite set of \emph{term} variables,
which are denoted as $[[x]]$, $[[y]]$, $[[z]]$, etc.
A list of objects (variables, types or terms) is denoted by
an overline arrow. For instance, $[[pas]]$ is a list of positive type variables, 
$[[nbs]]$ is a list of negative type variables, 
$[[args]]$ is a list of values, which are arguments of a function.
$[[fv(iP)]]$ and $[[fv(iN)]]$ denote the set of free variables 
in a type $[[iP]]$ and $[[iN]]$, respectively.

\bigskip

\ottgrammartabular{
  \ottiP\ottinterrule
  \ottiN\ottinterrule
  \ottv\ottinterrule
  \ottc\ottinterrule
}

@@

\subsection{Well-Formedness}
\ottdefnsWFT
\ottdefnsWFAT

@@

\subsection{Grammar}

\subsubsection{Variables and Types}
In the algorithmic system, we extend the grammar of types
by adding positive and negative \emph{algorithmic variables}
($[[α̂⁺]]$, $[[β̂⁺]]$, $[[γ̂⁺]]$, etc. and $[[α̂⁻]]$, $[[β̂⁻]]$, $[[γ̂⁻]]$, etc.).
They represent the unknown types, which will be inferred by the algorithm.
This way, we add two base cases to the grammar of 
positive and negative types, and use highlight to denote that the type
can potentially contain algorithmic variables.

\begin{definition}[Algorithmic Types]
  \hfill \\
\ottgrammartabular{
  \ottuP\ottinterrule
  \ottuN\ottinterrule
}
\end{definition}

\subsubsection{Contexts}

Unannotated set of algorithmic variables is denoted as $[[Ξ]]$,
and it is used in the anti-unification algorithm.
$[[Γ ; Ξ ⊢ uP]]$ and $[[Γ ; Ξ ⊢ uN]]$ are used to denote
that the algorithmic type is well-formed in the contexts
$[[Γ]]$ and $[[Ξ]]$, which means that each algorithmic variable
of the type is contained in $[[Ξ]]$, and each free non-algorithmic type variable
of the type is contained in $[[Γ]]$.

Typically each algorithmic variable is associated with a
context it must be instantiated in 
(i.e. the context in which the type replacing the variable must be well-formed).
This association is represented by an \emph{algorithmic variable context} $[[Θ]]$.
\begin{definition}[Algorithmic Context]
  \hfill \\
  Algorithmic Context $[[Θ]]$ is represented by a set of 
  entries of form $[[ α̂⁺[Γ] ]]$ and $[[ α̂⁻[Γ] ]]$,
  where $[[α̂⁺]]$ and $[[α̂⁻]]$ are algorithmic variables,
  and $[[Γ]]$ is a context in which they must be instantiated.
  We assume that no two entries associating the same variable
  appear in $[[Θ]]$.

  $[[dom(Θ)]]$ denotes the set of variables appearing in $[[Θ]]$:
  $[[dom(Θ)]] = \{ [[α̂±]] \mid [[α̂±[Γ] ]] \in [[Θ]] \}$.
\end{definition}

\subsubsection{Subsitutions}

Substitution that operates on algorithmic type variables is denoted as
$[[uσ]]$. It is defined as a total function from algorithmic 
type variables to non-algorithmic types, preserving the polarity.

The signature $[[Θ ⊢ uσ]]$ means that $[[uσ]]$ maps each algorithmic 
variable appearing in $[[Θ]]$ to a type well-formed in the corresponding
context; and for each variable not appearing in $[[dom(Θ)]]$, acts as identity.

\begin{definition}[Signature of Algorithmic Substitution]
  $[[Θ ⊢ uσ]]$ means that
  \begin{enumerate}
    \item for any $[[ α̂±[Γ] ∊ Θ]]$, $[[ Γ ⊢ [uσ]α̂± ]]$ and
    \item for any $[[ α̂± ∉ dom(Θ)]]$, $[[ [uσ]α̂± ]] =  [[ α̂± ]]$.
  \end{enumerate}
\end{definition}

Anti-unification substitution is denoted as $[[aus]]$ and $[[ausr]]$.
In contrast to algorithmic substitution $[[uσ]]$,
it only defined on the negative algorithmic variables, 
and it allows mapping algorithmic variables to
\emph{algorithmic} terms.

The pair of contexts $[[Γ]]$ and $[[Ξ]]$,
in which the results of the anti-unification substitutions 
are formed, is fixed for the whole substitution.
This way, $[[Γ; Ξ2 ⊢ aus : Ξ1]]$ means that $[[aus]]$ maps each negative algorithmic
variable appearing in $[[Ξ1]]$ to a term well-formed in $[[Γ]]$ and $[[Ξ2]]$.

\begin{definition}[Signature of Anti-unification substitution]
  $[[Γ; Ξ2 ⊢ aus : Ξ1]]$ means that
  \begin{enumerate}
    \item for any $[[ α̂⁻ ∊ Ξ1]]$, $[[ Γ; Ξ2 ⊢ [aus]α̂⁻ ]]$ and
    \item for any $[[ α̂⁻ ∉ Ξ1]]$, $[[ [aus]α̂⁻ = α̂⁻ ]]$.
  \end{enumerate}
\end{definition}

@@

\subsection{Substitution}

\begin{definition}[Substitution]
  Substitutions (denoted as $[[σ]]$) 
  are represented by total functions form variables to types, preserving the polarity. 
\end{definition}

\begin{definition}[Substitution Application]
  Substitution application (denoted as $[[ [σ]iP ]]$ or $[[ [σ]iN ]]$) 
  is defined congruently as follows:
  \begin{itemize}
    \item $[[ [σ]α⁺ ]] = [[σ]] ([[α⁺]])$;
    \item $[[ [σ]α⁻ ]] = [[σ]] ([[α⁻]])$;
    \item $[[ [σ]↓iN ]] = [[↓[σ]iN]]$;
    \item $[[ [σ]↑iP ]] = [[↑[σ]iP]]$;
    \item $[[ [σ]∃nas.iQ ]] = [[∃nas.[σ]iQ]]$, 
    \item $[[ [σ]∀pas.iN ]] = [[∀pas.[σ]iN]]$(here we assume that $[[nas]]$ and $[[pas]]$ are lists of fresh variables, 
      that is the variable capture never happens);
    \item $[[ [σ](iP → iN) ]] = [[ [σ]iP → [σ]iN ]]$.
  \end{itemize}
\end{definition}

\begin{definition}[Substitution Signature]
  The signature $[[Γ' ⊢ σ : Γ]]$ means that
  \begin{enumerate}
    \item for any $[[α± ∊ {Γ}]], [[ Γ' ⊢ [σ]α± ]]$; and
    \item for any $[[α± ∉ {Γ'}]], [[ [σ]α± = α± ]]$.
  \end{enumerate}
\end{definition}

A substitution can be restricted to a set of variables. 
The restricted substitution is define as expected. 
\begin{definition}[Subsitution Restriction]
  The specification $[[σ  | varset]]$ is defined as
  a function such that 
  \begin{enumerate}
    \item $[[σ|varset]]([[α± ]]) = [[σ]]([[α± ]])$, if $[[α± ]] \in [[varset]]$; and
    \item $[[σ|varset]]([[α± ]]) = [[α± ]]$, if $[[α± ]] \notin [[varset]]$.
  \end{enumerate}
\end{definition}

Two substitutions can be composed in two ways:
$[[σ2 ○ σ1]]$ corresponds to a consecutive application of $[[σ1]]$ and $[[σ2]]$,
while $[[σ2 <=< σ1]]$
depends on a signature of $[[σ1]]$ and modifies $[[σ1]]$ by applying
$[[σ2]]$ to its results on the domain.
\begin{definition}[Substitution Composition]
  $[[σ2 ○ σ1]]$ is defined as a function such that
  $[[σ2 ○ σ1]]([[α± ]]) = [[σ2]]([[σ1]]([[α± ]]))$.
\end{definition}

\begin{definition}[Monadic Substitution Composition]
  Suppose that $[[Γ' ⊢ σ1 : Γ]]$.
  Then we define $[[σ2 <=< σ1]]$ as $[[(σ2 ○ σ1)|{Γ}]]$.
\end{definition}

\begin{definition}[Equivalent Substitutions]
  The substitution equivalence judgement $[[Γ' ⊢ σ1 ≈ σ2 : Γ]]$ 
  indicates that on the domain $[[Γ]]$, 
  the result of $[[σ1]]$ and $[[σ2]]$ are equivalent in context $[[Γ']]$.
  Formally, for any $[[α± ∊ {Γ}]], [[ Γ' ⊢ [σ1]α± ≈ [σ2]α± ]]$.
\end{definition}

\input{../_build/_gen/tex/subst-lemmas.tex}

### 2023-08-08 proofs/tex/decl-subtyping-lemmas.tex
wip: leftovers

\begin{lemma}[Strong transitivity of subtyping] \label{lemma:subtyping-transitivity}
  Assuming all the types are well-formed in $[[Γ]]$,
  \begin{itemize}
    \item $-$ if $[[Γ ⊢ iN ≤ iM1]]$, $[[Γ ⊢ iM2 ≤ iK]]$, and for 
      $[[Γ' ⊢ σ : Γ]]$, $[[ [σ]iM1 = [σ]iM2 ]]$ then $[[Γ' ⊢ [σ]iN ≤ [σ]iK]]$
    \item $+$ if $[[Γ ⊢ iP ≥ iQ1]]$, $[[Γ ⊢ iQ2 ≥ iR]]$, and for
      $[[Γ' ⊢ σ : Γ]]$, $[[ [σ]iQ1 = [σ]iQ2 ]]$ then $[[Γ' ⊢ [σ]iP ≥ [σ]iR]]$
  \end{itemize}
\end{lemma}
\begin{proof}
  We prove it by induction on $\depth{[[Γ ⊢ iN ≤ iM1]]} + \depth{[[Γ ⊢ iM2 ≤ iK]]}$ and mutually, 
  on $\depth{[[Γ ⊢ iP ≥ iQ1]]} + \depth{[[Γ ⊢ iQ2 ≥ iR]]}$.

@@

      Notice that we can weaken and rearrange the contexts without changing the depths of the 
      derivations: $[[Γ, pbs, pcs ⊢ [iPs/pas]iN' ≤ iM1']]$
      and $[[Γ, pbs, pcs ⊢ [iQs/pbs]iM2' ≤ iK']]$. This way, 
      the sum of the depths of these derivations is smaller than the sum of the depths of
      $[[Γ ⊢ iN ≤ iM1]]$ and $[[Γ ⊢ iM2 ≤ iK]]$.
      Let us apply the induction hypothesis to these derivations, 
      with the substitution $[[ Γ', pcs ⊢ σ ○ (iQs/pbs) : Γ, pbs, pcs  ]]$
      (\cref{lemma:subst-domain-weakening}).
      To apply the induction hypothesis, it is left to show that 
      $[[ σ ○ (iQs/pbs) ]]$ unifies $[[iM1']]$ and $[[ [iQs/pbs]iM2']]$:
      $$
      \begin{aligned}[t]
        [[ [σ ○ iQs/pbs]iM1' ]] &= [[ [σ][iQs/pbs]iM1' ]]\\
                                &= [[ [ [σ]iQs/pbs ][σ]iM2' ]]
                                && \text{by \cref{lemma:subst-composition}}\\
                                &= [[ [ [σ]iQs/pbs ][σ]iM2' ]]
                                && \text{Since $[[ [σ]iM1' = [σ]iM2' ]]$}\\
                                &= [[  [σ][iQs/pbs]iM2' ]]
                                && \text{by \cref{lemma:subst-composition}}\\
                                &= [[  [σ][iQs/pbs][iQs/pbs]iM2' ]]
                                && \text{Since $[[Γ, pcs ⊢ iQs]]$, and $[[{(Γ, pcs)} ∩ {pbs} = ∅]]$ }\\
                                &= [[  [σ ○ iQs/pbs][iQs/pbs]iM2' ]]
      \end{aligned}
      $$
      This way the induction hypothesis gives us
      $[[ Γ', pcs ⊢ [σ][iQs/pbs][iPs/pas]iN' ≤  [σ][iQs/pbs]iK' ]]$,
      and since $[[Γ, pcs ⊢ iK']]$, $[[ [iQs/pbs]iK' = iK' ]]$, that is 
      $[[ Γ', pcs ⊢ [σ][iQs/pbs][iPs/pas]iN' ≤  [σ]iK' ]]$.
      Let us rewrite the substitution that we apply to $[[iN']]$:
      $$
      \begin{aligned}[t]
        [[ [σ ○ iQs/pbs ○ iPs/pas]iN' ]] &= [[ [ (σ <=< iQs/pbs) ○ σ ○ iPs/pas]iN' ]]
                                       && \text{by \cref{lemma:subst-composition}}\\
                                       &= [[ [(σ <=< iQs/pbs) ○ (σ <=< iPs/pas) ○ σ] iN' ]]
                                       && \text{by \cref{lemma:subst-composition}}\\
                                       &= [[ [(((σ <=< iQs/pbs) ○ σ) <=< iPs/pas) ○ σ] iN' ]]
                                       && \text{Since $[[fv([σ]iN') ∩ {pbs} = ∅]]$}\\
                                       &= [[ [((σ ○ iQs/pbs) <=< iPs/pas) ○ σ] iN' ]]
                                       && \text{by \cref{lemma:subst-composition}}\\
                                       &= [[ [(σ ○ iQs/pbs) <=< iPs/pas][σ] iN' ]]
      \end{aligned}
      $$
      Notice that $[[(σ ○ iQs/pbs) <=< iPs/pas]]$
      is a substitution that turns $[[pai]]$ into $[[ [σ ○ iQs/pbs]iPi ]]$, 
      where $[[ Γ',pcs ⊢ [σ ○ iQs/pbs]iPi]]$.
      This way, 
      $[[ Γ', pcs ⊢ [(σ ○ iQs/pbs) <=< iPs/pas][σ]iN' ≤  [σ]iK' ]]$
      means $[[Γ ⊢ ∀pas.[σ]iN' ≤ ∀pcs.[σ]iK']]$
      by \cref{lemma:quant-rule-decomposition}, that is
      $[[Γ ⊢ [σ]iN ≤ [σ]iK]]$, as required.
  \end{caseof}

@@

      Notice that the derivations of $[[Γ ⊢ iP ≥ iQ1]]$ and $[[Γ ⊢ iN' ≤ iM1']]$ are proper sub-derivations of
      $[[Γ ⊢ iP → iN' ≤ iQ1 → iM1']]$, and the derivations of $[[Γ ⊢ iQ2 ≥ iR]]$ and $[[Γ ⊢ iM2' ≤ iK']]$ are proper sub-derivations of
      $[[Γ ⊢ iQ2 → iM2' ≤ iR → iK']]$. This way, the induction hypothesis is applicable:
      \begin{itemize}
        \item applying the induction hypothesis to $[[Γ ⊢ iP ≥ iQ1]]$ and $[[Γ ⊢ iQ2 ≥ iR]]$ 
          with $[[Γ' ⊢ σ : Γ]]$ unifying $[[iQ1]]$ and $[[iQ2]]$, we obtain $[[Γ' ⊢ [σ]iP ≥ [σ]iR]]$;
        \item applying the induction hypothesis to $[[Γ ⊢ iN' ≤ iM1']]$ and $[[Γ ⊢ iM2' ≤ iK']]$ 
          with $[[Γ' ⊢ σ : Γ]]$ unifying $[[iM1']]$ and $[[iM2']]$, we obtain $[[Γ' ⊢ [σ]iN' ≤ [σ]iK']]$.
      \end{itemize}
      This way, by \ruleref{\ottdruleDOneArrowLabel}, $[[Γ' ⊢ [σ]iP → [σ]iN' ≤ [σ]iR → [σ]iK']]$,
      that is $[[Γ' ⊢ [σ]iN ≤ [σ]iK]]$, as required.
  \end{caseof}

  After that we consider all the 
  analogous positive cases, and prove them symmetrically.
\end{proof}

\begin{corollary}[Transitivity of subtyping] \label{corollary:subtyping-transitivity}
  Assuming the types are well-formed in $[[Γ]]$,
  \begin{itemize}
    \item[$-$] if $[[Γ ⊢ iN1 ≤ iN2]]$ and $[[Γ ⊢ iN2 ≤ iN3]]$ then $[[Γ ⊢ iN1 ≤ iN3]]$,
    \item[$+$] if $[[Γ ⊢ iP1 ≥ iP2]]$ and $[[Γ ⊢ iP2 ≥ iP3]]$ then $[[Γ ⊢ iP1 ≥ iP3]]$.
  \end{itemize}
\end{corollary}

>>>>

\begin{lemma}[Transitivity of subtyping] 
  \label{lemma:subtyping-transitivity}
  Assuming the types are well-formed in $[[Γ]]$,
  \begin{itemize}
    \item[$-$] if $[[Γ ⊢ iN1 ≤ iN2]]$ and $[[Γ ⊢ iN2 ≤ iN3]]$ then $[[Γ ⊢ iN1 ≤ iN3]]$,
    \item[$+$] if $[[Γ ⊢ iP1 ≥ iP2]]$ and $[[Γ ⊢ iP2 ≥ iP3]]$ then $[[Γ ⊢ iP1 ≥ iP3]]$.
  \end{itemize}
\end{lemma}
\begin{proof}
  To prove it, we formulate a stronger property, 
  which will imply the required one, taking $[[σ]] = [[Γ ⊢ id : Γ]]$.

    Assuming all the types are well-formed in $[[Γ]]$,
    \begin{itemize}
      \item[$-$] if $[[Γ ⊢ iN ≤ iM1]]$, $[[Γ ⊢ iM2 ≤ iK]]$, and for 
        $[[Γ' ⊢ σ : Γ]]$, $[[ [σ]iM1 = [σ]iM2 ]]$ then $[[Γ' ⊢ [σ]iN ≤ [σ]iK]]$
      \item[$+$] if $[[Γ ⊢ iP ≥ iQ1]]$, $[[Γ ⊢ iQ2 ≥ iR]]$, and for
        $[[Γ' ⊢ σ : Γ]]$, $[[ [σ]iQ1 = [σ]iQ2 ]]$ then $[[Γ' ⊢ [σ]iP ≥ [σ]iR]]$
    \end{itemize}

  We prove it by induction on $\size{[[Γ ⊢ iN ≤ iM1]]} + \size{[[Γ ⊢ iM2 ≤ iK]]}$ and mutually, 
  on $\size{[[Γ ⊢ iP ≥ iQ1]]} + \size{[[Γ ⊢ iQ2 ≥ iR]]}$.

@@

      Notice that we can weaken and rearrange the contexts without changing the sizes of the 
      derivations: $[[Γ, pbs, pcs ⊢ [iPs/pas]iN' ≤ iM1']]$
      and $[[Γ, pbs, pcs ⊢ [iQs/pbs]iM2' ≤ iK']]$. This way, 
      the sum of the sizes of these derivations is smaller than the sum of the sizes of
      $[[Γ ⊢ iN ≤ iM1]]$ and $[[Γ ⊢ iM2 ≤ iK]]$.
      Let us apply the induction hypothesis to these derivations, 
      with the substitution $[[ Γ', pcs ⊢ σ ○ (iQs/pbs) : Γ, pbs, pcs  ]]$
      (\cref{lemma:subst-domain-weakening}).
      To apply the induction hypothesis, it is left to show that 
      $[[ σ ○ (iQs/pbs) ]]$ unifies $[[iM1']]$ and $[[ [iQs/pbs]iM2']]$:
      $$
      \begin{aligned}[t]
        [[ [σ ○ iQs/pbs]iM1' ]] &= [[ [σ][iQs/pbs]iM1' ]]\\
                                &= [[ [ [σ]iQs/pbs ][σ]iM2' ]]
                                && \text{by \cref{lemma:subst-composition}}\\
                                &= [[ [ [σ]iQs/pbs ][σ]iM2' ]]
                                && \text{Since $[[ [σ]iM1' = [σ]iM2' ]]$}\\
                                &= [[  [σ][iQs/pbs]iM2' ]]
                                && \text{by \cref{lemma:subst-composition}}\\
                                &= [[  [σ][iQs/pbs][iQs/pbs]iM2' ]]
                                && \text{Since $[[Γ, pcs ⊢ iQs]]$, and $[[{(Γ, pcs)} ∩ {pbs} = ∅]]$ }\\
                                &= [[  [σ ○ iQs/pbs][iQs/pbs]iM2' ]]
      \end{aligned}
      $$
      This way the induction hypothesis gives us
      $[[ Γ', pcs ⊢ [σ][iQs/pbs][iPs/pas]iN' ≤  [σ][iQs/pbs]iK' ]]$,
      and since $[[Γ, pcs ⊢ iK']]$, $[[ [iQs/pbs]iK' = iK' ]]$, that is 
      $[[ Γ', pcs ⊢ [σ][iQs/pbs][iPs/pas]iN' ≤  [σ]iK' ]]$.
      Let us rewrite the substitution that we apply to $[[iN']]$:
      $$
      \begin{aligned}[t]
        [[ [σ ○ iQs/pbs ○ iPs/pas]iN' ]] &= [[ [ (σ <=< iQs/pbs) ○ σ ○ iPs/pas]iN' ]]
                                       && \text{by \cref{lemma:subst-composition}}\\
                                       &= [[ [(σ <=< iQs/pbs) ○ (σ <=< iPs/pas) ○ σ] iN' ]]
                                       && \text{by \cref{lemma:subst-composition}}\\
                                       &= [[ [(((σ <=< iQs/pbs) ○ σ) <=< iPs/pas) ○ σ] iN' ]]
                                       && \text{Since $[[fv([σ]iN') ∩ {pbs} = ∅]]$}\\
                                       &= [[ [((σ ○ iQs/pbs) <=< iPs/pas) ○ σ] iN' ]]
                                       && \text{by \cref{lemma:subst-composition}}\\
                                       &= [[ [(σ ○ iQs/pbs) <=< iPs/pas][σ] iN' ]]
      \end{aligned}
      $$
      Notice that $[[(σ ○ iQs/pbs) <=< iPs/pas]]$
      is a substitution that turns $[[pai]]$ into $[[ [σ ○ iQs/pbs]iPi ]]$, 
      where $[[ Γ',pcs ⊢ [σ ○ iQs/pbs]iPi]]$.
      This way, 
      $[[ Γ', pcs ⊢ [(σ ○ iQs/pbs) <=< iPs/pas][σ]iN' ≤  [σ]iK' ]]$
      means $[[Γ ⊢ ∀pas.[σ]iN' ≤ ∀pcs.[σ]iK']]$
      by \cref{lemma:quant-rule-decomposition}, that is
      $[[Γ ⊢ [σ]iN ≤ [σ]iK]]$, as required.
  \end{caseof}

@@

      Notice that the derivations of $[[Γ ⊢ iP ≥ iQ1]]$ and $[[Γ ⊢ iN' ≤ iM1']]$ are proper sub-derivations of
      $[[Γ ⊢ iP → iN' ≤ iQ1 → iM1']]$, and the derivations of $[[Γ ⊢ iQ2 ≥ iR]]$ and $[[Γ ⊢ iM2' ≤ iK']]$ are proper sub-derivations of
      $[[Γ ⊢ iQ2 → iM2' ≤ iR → iK']]$. This way, the induction hypothesis is applicable:
      \begin{itemize}
        \item applying the induction hypothesis to $[[Γ ⊢ iP ≥ iQ1]]$ and $[[Γ ⊢ iQ2 ≥ iR]]$ 
          with $[[Γ' ⊢ σ : Γ]]$ unifying $[[iQ1]]$ and $[[iQ2]]$, we obtain $[[Γ' ⊢ [σ]iP ≥ [σ]iR]]$;
        \item applying the induction hypothesis to $[[Γ ⊢ iN' ≤ iM1']]$ and $[[Γ ⊢ iM2' ≤ iK']]$ 
          with $[[Γ' ⊢ σ : Γ]]$ unifying $[[iM1']]$ and $[[iM2']]$, we obtain $[[Γ' ⊢ [σ]iN' ≤ [σ]iK']]$.
      \end{itemize}
      This way, by \ruleref{\ottdruleDOneArrowLabel}, $[[Γ' ⊢ [σ]iP → [σ]iN' ≤ [σ]iR → [σ]iK']]$,
      that is $[[Γ' ⊢ [σ]iN ≤ [σ]iK]]$, as required.
  \end{caseof}
  After that we consider all the 
  analogous positive cases, and prove them symmetrically.
\end{proof}
